---
title: "Lab 2"
author: "[your name here]"
date: "`r format(Sys.time(), '%d/%m/%y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r preamble}
# Load packages


# Read data

```

## Types of variables


```{r pipe-1}
# Using base R pipe
1 |> sum(1)
1 |> sum(1) |> sum(5)
```

```{r pipe-2}
# Using tidyverse pipe
1 %>% sum(1)
1 %>% sum(1) %>% sum(5)
```

## Black lives matter!

### Examine the data

```{r glimpse}

```

### Data wrangling

```{r subset}

```


```{r glimpse-again}

```

```{r coerce}
police_2 <- police_2 |> mutate(age = as.numeric(age))


```

You can put your text cursor on a line below and press `Ctrl+Alt+I` on the keyboard to create a new code block. Alternatively, from the menu bar at the top of RStudio, you can select `Code > Insert Chunk`.



## Activities

Discuss with your neighbour or tutor:

1. What is the main purpose of the `select()` and `filter()` functions?

2. What does coerce mean in the context of R? and Why do we need to coerce some variables?

3. What is the `mutate()` function useful for?

Using the `police_2` dataset:

1. Filter how many observations are ‘White’ in the `raceethnicity` variable? How may rows/observations are left?

2. How many ‘Hispanic/Latino’ are there in the dataset?

3. Using the example of Figure 2.3, could you filter how many were killed that were (a) ‘Black’ and (b) killed by firearm (‘firearm’)?

4. What about ‘White’ and ‘firearm’?