---
title: "Lab 2"
author: "[your name here]"
date: "`r format(Sys.time(), '%d/%m/%y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r preamble}
# Load packages


# Read data
```

## Types of variables

```{r iris-glimpse}
glimpse(iris)
```

```{r iris-levels}

```

```{r starwars-glimpse}
starwars2 <- starwars[, 1:11]
glimpse(starwars2)
```


```{r starwars-factor}

```

```{r starwars-glimpse2}

```

## Pipes

```{r pipe-1}
# Using base R pipe
1 |> sum(1)
1 |> sum(1) |> sum(5)
```

```{r pipe-2}
# Using tidyverse pipe
1 %>% sum(1)
1 %>% sum(1) %>% sum(5)
```

## Black lives matter!



## Activities

Discuss with your neighbour or tutor:

1. What is the main purpose of the `select()` and `filter()` functions?

2. What does coerce mean in the context of R? and Why do we need to coerce some variables?

3. What is the `mutate()` function useful for?

Using the `police_2` dataset:

1. Filter how many observations are ‘White’ in the `raceethnicity` variable? How may rows/observations are left?

2. How many ‘Hispanic/Latino’ are there in the dataset?

3. Using the example of Figure 2.3, could you filter how many people were killed that were (a) ‘Black’ and (b) possessed a firearm on them at the time (‘Firearm’)?

4. What about ‘White’ and ‘Firearm’?

Finally, 'Knit' your R Markdown file.
