---
title: "Lab 1"
output: html_document
---

## R as calculator

```{r sum-1}
2 + 2
```

```{r sum-2}

```

## Testing logical operators

```{r logical-1}
10 == 10
10 != 10
```

```{r logical-2}

```

## Assigning values to 'objects'

```{r assign-1}
a <- 10
a + 5
```

```{r assign-2}

```

### Code Order

```{r order-1}
a + 2
```

```{r order-2}
a <- a + 5
a
```

## Activity

1. What are the main differences between working in a `R Markdown` file (pane 1) and directly on the console (pane 3)?


2. Can you describe what happens when your run the following code chunk? (tip: look at the environment tab in pane 2)

```{r}
object1 <- 10
object2 <- 30
```

3. Click the 'Knit' button in the bar at the top of the R Markdown file (pane 1). This will turn your R Markdown file into an HTML document.

4. Create a new code chunk, you can put your text cursor on a line below and press `Ctrl+Alt+I` on the keyboard. Alternatively, from the menu bar at the top of RStudio, you can select `Code > Insert Chunk`.

